---
title: "Alcohol vs Seat choice"
author: "Karen"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
According to the boxplot, the median for the amount of alcohol consumed in the back seat is about 4. The median for the amount of alcohol consumed in the from the front seat is 0 and the middle seat is about 1. Alcohol is consumed more in the back seat then the front and middle.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This fancy box plot agrees with the box plot demonstrated earlier. It shows that on average the students in the back seats consume more alcohol than the students in the front seat. It also shows that the standard deviation (the variation) of alcohol consumed by the back-seat students is greater than the front and middle seat students. This is represented in the notches of the fancy box plot showing a bigger notch for the backseat students and smaller notches for the front and middle seat students.  

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical data displays the exact averages. The front seat students drink 1.8 times per week, the middle seat students drink 3.3 times per week, and the back seat students drink 8.6 times per week. This data further agrees with the two box plots represented before. It also shows that the standard deviation of the front, middle, and back seats are 3.8, 6.2, and 12.6 respectively. Which proves that the further a student is seated in the class, the more times they consume alcohol per week.  

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

This anova test shows a low p-value which means that there are at least two rows where the alcohol consumption is significantly different between each row (front, middle,and back). Therefore, we need to perform another test to see which rows are different from each other.

```{r}
plot(TukeyHSD(model1))
```

This TuckeyHSD model shows that the differences in the mean level of drinking between the back and the front rows is between 12 to 4 times of alcohol per week in the back compared to the front.The comparison between the back rows and the middle rows is that the back rows are drinking about 10 to 3 times more than the middle. It also shows that the front and middle rows are not too different from each other because the third line cuts through the number 0. 

## Conclusions


